---
title: "Exploratory Data Analysis"
author: "Lubov McKone"
format: 
  revealjs:
    chalkboard: true
editor: visual
toc: true
bibliography: references.bib
execute: 
  warning: false
code-annotations: hover
---

## Introduction

```{r}
#| include: false

library(medicaldata)
library(dplyr)
library(ggplot2)
library(reticulate)

scurvy <- medicaldata::scurvy 
```

This is a notebook for the Scurvy Lab at JHU to share code and results. The Scurvy Lab studies the efficacy of different nutrients on treating scurvy. Data for this study comes from [@lindst1953]. Data was collected from `{r} unique(scurvy$study_id)` participants.

## Data Processing

This is where we will process our data for analysis.

```{r}
#| code-fold: true
#| echo: true


scurvy_processed <- scurvy |>
  mutate_at(c(4:8), # <1>
            ~as.numeric(substr(., start = 1, stop = 1))) # <2>
```

1.  For columns that represent severity of symptoms on day 6
2.  Extract only the first character, and convert to numeric

## Exploratory Data Analysis

This is where we will explore our data.

::: panel-tabset
## Gum Rot

```{r}
#| label: fig-gum-rot


scurvy_processed |>
  group_by(treatment) |>
  summarise(gum_rot_severity = mean(gum_rot_d6)) |>
  ggplot() +
  geom_col(aes(treatment, gum_rot_severity))
```

## Skin Sores

```{python}
#| label: fig-skin-sore

scurvy_processed = r.scurvy_processed

scurvy_processed.groupby('treatment').skin_sores_d6.mean().plot(kind = "bar")

```

## Knee Weakness

## Lassitude
:::

## Discussion

As seen in @fig-gum-rot and @fig-skin-sore, citrus is the best treatment for scurvy.
